\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2018-02-11 doc/USER_MANUAL/01_introduction.tex
added description of Hourglass modes that can appear in some cases in the source element to the users manual

>>>>

\red{Beware that, in a spectral-element method, some spurious modes (that have some similarities with classical so-called "Hourglass modes" in finite-element techniques,
although in the SEM they are not zero-energy modes) can appear in some (but not all) cases in the spectral element in which the source is located.
Fortunately, they do not propagate away from the source element.
However, this means that if you put a receiver in the same spectral element as a source, the recorded signals may in some cases be wrong, typically exhibiting some spurious
oscillations, which are often even non causal.
If that is the case, an easy option is to slightly change the mesh in the source region in order to get rid of these Hourglass-like spurious modes,
as explained in \cite{DuLiScGa14}, in which this phenomenon is described in details, and in which practical solutions to avoid it are suggested.}\\
